Winter 2025 ToDo

### 2025-12-16 Relations/Paper/Winter_2025_TODO.tex
todo update prior to meeting Tue 16th Dec

\section*{Week starting 8th December}
\begin{todolist}
  \item [\done] Is the new definition of wdec in Predicates correct? It corresponds to the definition in FBranching. (Do we want to go through and update all uses of Wdec with the new definition if it is correct?)
  \item [\done] Go through the locations where we could use the wdec definition and replace it with our new wdec definition (search for wdec, previously we've manually defined it in each location)
  \item $\lnot \lnot $closed C definition sometimes is a lambda term with three variables we can refactor this in those locations. (low priority) 
  \item can we show that  wfminDNE implies RisDec. We've shown that WFmin implies RisDec (in WFcounters). We've started the DNE proof in Wfimplications (commented out). 
  \item [\done] We successfully proved that RisWFmin implies RisDec and RisMinDec!
  \item We're trying to show that wfminDNE implies WEM (in WFcounters) (this is where we ended the session 9th December). We currently think it is not possible.

  \item [\done] We have made new discoveries as to what WFmin can imply. Can we use these developments to go from WFmin to WFacc? For example, with the addition of EM. Reminder that WFmin implies EM when R is non empty.
  \item (high priority) Having shown that WFmin implies WFacc when R is non empty we need to update the paper. Specifically we should update the text in the WF section and the diagram to incorporate the new implication.  Update the table too with R not empty? 
  \item [\done] Show that we can go from our weakest WF definition to our strongest
  \item Do we want to make explicit on our table in the paper that we can go from our weakest definition (wfcornotnot) to our strongest (wfmin) via classical assumptions (EM). We think we already mention that all the definitions are classically equivalent in the paper (do we?).  
  \item We have moved the proof of wfmin implies EM to WFbasic implications. Can delete the old proof in WFcounters. 
  \item can we show that wfminnotnot implies wfaccnotnot? That would give a nice equivalence between three definitions in the weak row of the diagram. One approach could be to see what predicates we can prove with just wfminnotnot (in the same way that we first explored what predicates could be proved with wfmin before finding out a path to wfacc). Perhaps wfminnotnot implies WEM?
  \item Work out what if any WF definition implies WEM (other than WFmin)?
  \item Get rid of wfcor+ in our main development, substitute in the not not definition for consistency.

@@

  \item TRS: Complete our formalization. formalize some simple TRS to check our implementation works. 
  \item TRS: Formalize orthogonality and show it is equivalent to our notion of confluence. 
  \item [\done] We've shown that wfminDNE gives us decRmin is we have decidability of equality. 
  \item [\done] We've shown that wfminDNE along with decidability of equality and not not closure of R gives us R is MinDec.
  \item [\done] We show that R is weakly decidable with the assumption of wfminDNE and equality decidability.
  \item Can we show that the not not closure of R emerges from WFminDNE?
  \item Shown wfmindne not not implies wfacc not not with accDNE. Now need to update the paper/graph to reflect this.

>>>>

\section*{Week starting 8th December}
\begin{todolist}
  \item [\done] Is the new definition of wdec in Predicates correct? It corresponds to the definition in FBranching. (Do we want to go through and update all uses of Wdec with the new definition if it is correct?)
  \item [\done] Go through the locations where we could use the wdec definition and replace it with our new wdec definition (search for wdec, previously we've manually defined it in each location)
  \item $\lnot \lnot $closed C definition sometimes is a lambda term with three variables we can refactor this in those locations. (low priority) 
  \item can we show that  wfminDNE implies RisDec. We've shown that WFmin implies RisDec (in WFcounters). We've started the DNE proof in Wfimplications (commented out). 
  \item [\done] We successfully proved that RisWFmin implies RisDec and RisMinDec!
  \item [\done] We're trying to show that wfminDNE implies WEM (in WFcounters) (this is where we ended the session 9th December). We currently think it is not possible.

  \item [\done] We have made new discoveries as to what WFmin can imply. Can we use these developments to go from WFmin to WFacc? For example, with the addition of EM. Reminder that WFmin implies EM when R is non empty.
  \item (high priority) Having shown that WFmin implies WFacc when R is non empty we need to update the paper. Specifically we should update the text in the WF section and the diagram to incorporate the new implication.  Update the table too with R not empty? 
  \item [\done] Show that we can go from our weakest WF definition to our strongest
  \item Do we want to make explicit on our table in the paper that we can go from our weakest definition (wfcornotnot) to our strongest (wfmin) via classical assumptions (EM). We think we already mention that all the definitions are classically equivalent in the paper (do we?).  
  \item [\done] We have moved the proof of wfmin implies EM to WFbasic implications. Can delete the old proof in WFcounters. 
  \item can we show that wfminnotnot implies wfaccnotnot? That would give a nice equivalence between three definitions in the weak row of the diagram. One approach could be to see what predicates we can prove with just wfminnotnot (in the same way that we first explored what predicates could be proved with wfmin before finding out a path to wfacc). Perhaps wfminnotnot implies WEM?
  \item [\done] Work out what if any WF definition implies WEM (other than WFmin)?
  \item [\done] Get rid of wfcor+ in our main development, substitute in the not not definition for consistency.

@@

  \item TRS: Complete our formalization. formalize some simple TRS to check our implementation works. 
  \item TRS: Formalize orthogonality and show it is equivalent to our notion of confluence. 
  \item [\done] We've shown that wfminDNE gives us decRmin is we have decidability of equality. 
  \item [\done] We've shown that wfminDNE along with decidability of equality and not not closure of R gives us R is MinDec.
  \item [\done] We show that R is weakly decidable with the assumption of wfminDNE and equality decidability.
  \item Can we show that the not not closure of R emerges from WFminDNE?
  \item We have shown wfmindne not not implies wfacc not not with accDNE. Now need to update the paper/graph to reflect this.
